%===============================================================================
\RequirePackage[l2tabu, orthodox]{nag}  % Complain about outdated commands.

\documentclass[11pt,a4paper]{moderncv}
\moderncvtheme[blue]{classic}
% Banking theme is more compact and eliminates the picture.
%\moderncvtheme[blue]{banking}

\usepackage{moderntimeline}
% Set the scale.
\tlmaxdates{2010}{2020}
% Set the line width.
% This automatically sets the space under the top label to be 1pt more
\tlwidth{0.6ex}
% Set the labels text size
\tltext{\footnotesize}

\usepackage[T1]{fontenc}
% character encoding
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}

% adjust the page margins
\usepackage[scale=0.8]{geometry}
\recomputelengths% required when changes are made to page layout lengths

% Activate to begin paragraphs with an empty line rather than an indent
%\usepackage[parfill]{parskip}
\usepackage{graphicx}
    \graphicspath{ {./images/}}
    % Set default image width. This will disrupt scale settings.
    \setkeys{Gin}{width=0.9\linewidth}
    % Allow conversion of eps to pdf format. For pdflatex.
    % May need to give write permission to terminal.
    % pdflatex -shell-escape <file>.
    \usepackage{epstopdf}

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{microtype}  % Improve spacing between words and letters.
\usepackage{cleveref}
\DeclareGraphicsRule{.tif}{png}{.png}
    {`convert #1 `dirname #1`/`basename #1.tif`.png}



% Fancy page numbering
% Maybe this is dependent on LaTeX build and version of moderncv?
% Remove these for troubleshooting.
\usepackage{fancyhdr}
\usepackage{lastpage}
\fancyfoot{} % clear all footer fields
\fancyfoot[LE,RO]{\thepage}           % page number in "outer" position of footer line
\fancyfoot[RE,LO]{\footnotesize } % other info in "inner" position of footer line
\pagestyle{fancy}
\rfoot{\thepage\ of \pageref{LastPage}}

% -----------------------------------
% BIBLIOGRAPHY
%\usepackage[style=alphabetic,sorting=ynt,backend=biber]{biblatex}
\usepackage[
	style=numeric,
	backend=biber,
	doi=false,
	url=false,
	isbn=false
]{biblatex}
\addbibresource{sample.bib}
% -----------------------------------

% -----------------------------------
 % PERSONAL DATA
\firstname{Sam}
\lastname{Castle}
%\title{Curriculum Vitae}               % optional, remove the line if not wanted
\title{Computer Science Researcher}
\address{185 Stevens Way}{Box 352350}{Seattle, WA 98195}    % optional, remove the line if not wanted
%\mobile{+1 864-207-6285}                    % optional, remove the line if not wanted
%\phone{<Phone number>}                      % optional, remove the line if not wanted
\email{stcastle@cs.washington.edu}                      % optional, remove the line if not wanted
\extrainfo{\url{www.samcastle.com}} % optional, remove the line if not wanted
% add github
%\photo[84pt]{small-sam-michael-wedding.png}                % '64pt' is the height the picture must be resized to and 'picture' is the name of the picture file; optional, remove the line if not wanted
%\quote{``Success is the ability to go from failure to failure without losing your enthusiasm.'' --- Winston Churchill}    % optional, remove the line if not wanted
%\quote{Practical, Purposeful, Passionate Research.}
% -----------------------------------

%\nopagenumbers{}                             % uncomment to suppress automatic page numbering for CVs longer than one page


%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
\maketitle

\vspace{-10mm}

% -----------------------------------------------
% SUMMARY
\section{Summary}
\cvline{}{
  %\small I am a current PhD student in
  %\href{http://www.cs.washington.edu}{Computer Science at the University of
  %Washington.}
  My research focuses on how technology can improve the lives of underserved
  populations in low-income regions.
  This involves work in in Computer Security and Privacy, HCI, Systems,
  Networks, and Data Analytics.
}
% -----------------------------------------------

% -----------------------------------------------
% OBJECTIVE
%\section{Objective}
%\cvline{}{\Large <Desidered employment>}
%\cvline{}{\small <summary>}
% -----------------------------------------------

% -----------------------------------------------
% EDUCATION
\section{Education}

\tlcventry{2015}{0}{PhD in Computer Science}
{\href{http://cs.washington.edu}{University of Washington}}{Seattle}{WA}
{\href{http://ictd.cs.washington.edu/people.html}{ICTD Lab}:
Information and Communication Technologies for Development
}

\tlcventry{2010}{2015}{BS in Mathematics}{Davidson College}{Davidson}{NC}
{Summa Cum Laude, Overall GPA:~4.00 out of 4.00\\
Minor in Astrophysics} % arguments 3 to 6 are optional
% -----------------------------------------------

% -----------------------------------------------
% RESEARCH PROJECTS
\section{Research Projects}

\subsection{Current}
%\cvline{}{\textbf{Branchless Banking Android Applications}}
\tlcventry{2016}{0}{Branchless Banking Android Applications}{}{}{}
{We are developing a prototype Android application for branchless banking with
a focus on security and privacy in the developing world.
We focus on server [mis]configurations and propose an OpenSSL wrapper library.
Future work will survey the developers who are working on deployed branchless banking applications.}

\tlcventry{2016}{0}{Digital Financial Services: Literature Review}{}{}{}{
We are conducting a survey of research in financial services for the unbanked published in mainstream Computer Science literature.
The white paper will soon be available at \href{http://ictd.cs.washington.edu}{http://ictd.cs.washington.edu}.
}

%\subsection{Previous}

% -----------------------------------------------

% -----------------------------------------------
% WORK EXPERIENCE
\section{Work Experience}

\subsection{Teaching}
\vspace{-3mm}

\tldatelabelcventry{2015}{Fall 2015}{CSE 311: Foundations of Computing I}
{University of Washington}{Seattle}{WA}
{
\begin{itemize}
  \item[--] Teaching Assistant under James Lee and Shayan Oveis Gharan.
  \item[--] Taught a weekly section of 30 students.
  \item[--] Led weekly office hour instruction.
\end{itemize}
} % end tlcventry

\vspace{1mm}
\subsection{Internships}
\vspace{-3mm}

\tldatelabelcventry{2015}{Sp 2015}{NSF REU Student}{Cerro Tololo
Inter-American Observatory}{La Serena}{Chile}
{Developed Automated image processing tools in Python to study the
shell elliptical galaxy NGC 3923.}

%\tlcventry[blue]{2006}{0}{Systems Engineer}{\href{http://www.nga.gov}{NGA}}
\tlcventry{2013}{2014}{Modeling \& Simulation Intern}{\href{http://www.nga.mil}{National Geospatial-Intelligence Agency (NGA)}}{Department of Defense}{USA}
{Summers 2013 and 2014.
\begin{itemize}
	\item[--] Worked with technical subject matter and tools in the application
  of information technology for modeling and simulation.
\end{itemize}} % end tlcventry

\tldatelabelcventry{2012}{Fall 2012}{Meteor Physics Intern}{NASA Marshall Space Flight Center}{Huntsville}{AL}
{Researched the particle size distribution of fragmenting meteors and assisted
the \href{https://www.nasa.gov/offices/meo/home/index.html}{NASA Meteoroid
Environment Office.}}

% END WORK EXPERIENCE
% -----------------------------------------------

% -----------------------------------------------
% TECHNICAL SKILLS
\section{Technical Skills}

% Development
\subsection{Development}
%\cvline{Languages}{Java, C++, Python, Perl, MATLAB, Mathematica, Android, Shell/Bash, GNU Make}
\cvcomputer{Languages}{Java, C++, Python, Perl, MATLAB, Mathematica, Android, Shell/Bash, GNU Make}
{Web}{HTML, CSS, JavaScript, Bootstrap, PHP}
\cvcomputer{Methods}{Object-Oriented Programming, Machine Learning, Formal Verification}
{Databases}{SQL, MySQL}

% Systems and Network Administration
\subsection{Systems and Network Administration}
\cvcomputer{Operating Systems}{GNU/Linux (Debian, Ubuntu, Fedora), MacOS X, Windows}
{Security}{SSL/TLS, PGP, OTR, OpenSSL, Tor}
\cvcomputer{Web}{Apache}
{Virtualization}{VNC, Wine}

% Office and tools
\subsection{Office and tools}
\cvcomputer{Office}{OpenOffice/LibreOffice, Microsoft Office, Gimp}
{Editing}{\LaTeX, Vim, Emacs, Eclipse IDE}
\cvcomputer{Management}{Git, GitHub}
{Tools}{Gnuplot, Wine}

% END TECHNICAL SKILLS
% -----------------------------------------------


% -----------------------------------------------
% PUBLICATIONS
%\section{Publications}
%\nocite{*}
%\printbibliography[heading=none]
% -----------------------------------------------

% -----------------------------------------------
% FOREIGN LANGUAGES
\section{Foreign Languages}
\cvline{English}{Native \hfill \emph{Mother tongue}}
\cvline{German}{Minimum Professional Proficiency \hfill \emph{5 years in school, foreign exchange program}}
\cvline{Spanish}{Elementary Proficiency \hfill \emph{Studied abroad in Chile, occasional practice}}
% Another possibility
%\cvcomputer{German}{Minimum Professional Proficiency} {}{\emph{Studied 5 years in school, teaching assistant, foreign exchange program}}
% -----------------------------------------------

% -----------------------------------------------
% PERSONAL
\section{Personal}
\cvline{Memberships}{Phi Beta Kappa, Sigma Pi Sigma, Omicron Delta Kappa}
\cvline{Offices}{Defense Advisor to Davidson College Honor Council (2013-2014), President of Davidson Outdoors (2013)}
\cvline{Hobbies}{Hiking, cycling, soccer, reading}
% -----------------------------------------------


\begin{tikzpicture}[remember picture,overlay]
      \node[anchor=south, yshift=0.25cm] at (current page.south) {\textit{Last update: \today}};
\end{tikzpicture}

\end{document}
